### 2020-07-01 manuscript/manuscript.rmd
use ggsave to save raw figures for Figure2 and Extended fig3

taxon_rectangles %>%
  ggplot() +
    scale_x_continuous(name = "Gene sampling") +
    scale_y_continuous(name = "Taxa sampling") +
    geom_rect( mapping = aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = clade )) +
    scale_fill_manual(values = clade_colors, guide = guide_legend(reverse = TRUE)) +
    facet_wrap( ~ matrix ) + theme_classic()

@@

@@

ggarrange(ggarrange(p1, p2, ncol = 2, labels = c("A", "B")), nrow = 3,
          p3, p4, labels = c("C", "D"))
```
**Fig. 4.**  Sensitive analyses with representative data matrices analyzed by different number of substitutionary categories (nCAT) in PhyloBayes. Statistical support values (posterior probabilities) were obtained from three data matrcies using the site-heterogeneous Poisson-CAT model with different categories” (A) Phlippe2009_Choanozoa; (B) Philippe2009_Holozoa; (C) Whelan2017_full_Choanozoa; (D) Whelan2017_strict. Statistical support for Ctenophora-sister and Porifera-sister is indicated in orange and green, respectively. Support values are from the sensitive analyses are shown in Supplementary Table 6.

@@

@@

@@

###```{r figure_phylogenetic_signal, fig.width=6, fig.height=12}

#au_tests %>%
#  unite(Matrix, c(manuscript, matrix, model)) %>%
#  group_by(Matrix, result) %>%
#  count() %>%
#  group_by(Matrix) %>%
#  mutate(percent = prop.table(n)) %>%
#  ggplot(aes(x = Matrix, y = percent, fill = result)) +
#    geom_bar(stat = "identity") +
#    scale_fill_manual(values = c("#E69F00", "#ebd196", "#a2e8d5", "#009E73")) +
#    coord_flip() +
#    theme(axis.text.y = element_blank(), axis.title.y = element_blank())

#```

![](figures/Figure_phylogenetic_signal.png)

>>>>

p =taxon_rectangles %>%
  ggplot() +
    scale_x_continuous(name = "Gene sampling") +
    scale_y_continuous(name = "Taxa sampling") +
    geom_rect( mapping = aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = clade )) +
    scale_fill_manual(values = clade_colors, guide = guide_legend(reverse = TRUE)) +
    facet_wrap( ~ matrix ) + theme_classic()

ggsave("figures/Figure2_raw.pdf", width=7.2, height=7.2)

```
![](figures/Figure_2_manuscript.png)

@@

ggsave("figures/Figure3_raw.pdf", width=7.2, height=3.6)
```

@@

ggarrange(ggarrange(p1, p2, ncol = 2, labels = c("A", "B")), nrow = 3,
          p3, p4, labels = c("C", "D"))

ggsave("figures/Figure4_raw.pdf", width=7.2, height=7.2)

```
**Fig. 4.**  Sensitive analyses with representative data matrices analyzed by different number of substitutionary categories (nCAT) in PhyloBayes. Statistical support values (posterior probabilities) were obtained from three data matrcies using the site-heterogeneous Poisson-CAT model with different categories” (A) Phlippe2009_Choanozoa; (B) Philippe2009_Holozoa; (C) Whelan2017_full_Choanozoa; (D) Whelan2017_strict. Statistical support for Ctenophora-sister and Porifera-sister is indicated in orange and green, respectively. Support values are from the sensitive analyses are shown in Supplementary Table 6.

@@

ggsave("figures/Extended_Data_Fig1_raw.pdf", width=20, height=12)

@@

ggsave("figures/Extended_Data_Fig2_raw.pdf", width=10, height=4)

@@

```{r figure_phylogenetic_signal, fig.width=6, fig.height=12}

p=au_tests %>%
  unite(Matrix, c(manuscript, matrix, model)) %>%
  group_by(Matrix, result) %>%
  count() %>%
  group_by(Matrix) %>%
  mutate(percent = prop.table(n)) %>%
  ggplot(aes(x = Matrix, y = percent, fill = result)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c("#E69F00", "#ebd196", "#a2e8d5", "#009E73")) +
    coord_flip() +
    theme(axis.text.y = element_blank(), axis.title.y = element_blank())

ggsave("figures/Extended_Data_Fig3_raw.pdf", width=6, height=12)

![](figures/Extended_Data_Fig3_manuscript.png)
